SPIRAL OPTIMIZATION ALGORITHM

### 2021-10-17 Semester I/Analisis Numerik Lanjut/Tugas Kerang/spiral.Rmd
contour new'

```{r,include=FALSE}
gambar_con = function(f,a,b){
  # generate
  x = seq(a,b,by = 0.25)
  # data frame
  temp_plot = 
    expand.grid(x,x) %>%
    as.data.frame() %>%
    rename(x = Var1,
	   y = Var2) %>%
    mutate(z = f(x,y)) %>%
  # bikin plot
  temp_plot 
#    ggplot(aes(x = x,
#	       y = y,
#	       z = z)) +
#    geom_contour() +
#    geom_contour_filled() 
}
```

@@

```{r,echo=FALSE,fig.retina=10}
f1 = function(x1,x2){cos(2* x1) - cos(2*x2) - 0.4}
gambar_con(f1,-10,10)
```

>>>>

```{r,include=FALSE}
ikanx = function(f,a,b){
  x = seq(a,b,by = .25)

  temp_plot =
    expand.grid(x,x) %>%
    rename(x = Var1,
           y = Var2) %>%
    mutate(z = f(x,y))

  temp_plot %>%
     ggplot(aes(x = x,y = y,z = z)) +
     geom_contour()
}

@@

```{r,echo=FALSE,fig.retina=10}
f1 = function(x1,x2){cos(2* x1) - cos(2*x2) - 0.4}
ikanx(f1,-10,10)
```
